Social Participation Ontology: community documentation, enhancements and use examples

### 2015-09-17 plosOne/plos.tex
started separating figures

\begin{table*}
  \centering
  \caption{New classes considered for expansion of the \ops. The taxonomic organization of these classes, within \ops\ can be observed in Figure~\ref{fig:owlExp}. Further information is in Section~\ref{downwards}.}
  \begin{tabular}{|l|l|p{5cm}|p{5cm}|}\hline
{\bf new class} & {\bf subclass of} & {\bf description} & {\bf further notes} \\\hline\hline
SocialNetwork & Organization & a social structure made up of social actors (such as individuals or organizations) and a set of dyadic ties between these actors & --//--\\\hline
FreeScaleNetwork & SocialNetwork & a network whose connectivity follows a power law & disjoint with UniformrandomNetwork and GeographicNetwork \\ \hline
ErdosRenyiNetwork & SocialNetwork & also known as Poisson network, this network sets, with equal propability, an edge between each pair of nodes & disjoint with FreeScaleNetwork and GeographicNetwork\\\hline
GeographicNetwork & SocialNetwork & a network whose connectivity is related to the distance of nodes in a metric space & Disjoint with both FreeScaleNetwork and ErdosRenyiNetwork \\\hline
SmallWorldNetwork & SocialNetwork & a network where most nodes can be reached from other nodes with few hops or steps & not disjoint with FreeScaleNetwork, ErdosRenyiNetwork and GeographicNetwork\\\hline\hline
InformalOrganization & Organization & an organization that is not formalized & disjoint with Intitution \\ \hline
Mob & InformalOrganization & a crowd of individuals & --//-- \\\hline
GiantMob & Mob & a crowd with more than 10,000 individuals & --//--\\\hline
DownloadedMob & Mob & a Mob convoqued by a network & this is a defined class, by being a network and being the subject of the relation convoquedBy with object Network \\ \hline\hline
Institution & Organization & a mechanism of social order that governs a set of individuals & disjoint with InformalOrganization \\\hline
PublicInstitution & Institution & an institution backed through public funds and controlled by the state & disjoint with Private Institution \\ \hline
PrivateInstitution & Institution & an institution backed through private fundings and controlled by private parties & disjoint with PublicInstitution \\ \hline
AcademicInstitution & Institution & an institution dedicated to education and research, which grants academic degrees & --//-- \\ \hline
NGO & Institution & a legally consituted corporation created by natural or legal people that operate independently from any form of government & --//-- \\\hline
SpuriousInstitution & Institution & an institution that holds prominent illegitimate or corrupt characteristcs & --//-- \\\hline
ExoticInstitution & Institution & an institution that does not fit previous classes or is characterized by a very unique traces & --//-- \\\hline\hline
VoluntaryExecutor & Executor & an executor that receives no formal reward for the tasks & disjoint with PaidExecutor \\ \hline
PaidExecutor & Executor & an Executor that receives formal reward for the tasks accomplished & a defined class, being an Executor and the subject of a receivesFrom predicate with SocialActor as object\\ \hline
  \end{tabular}
  \label{ospFooClass}
\end{table*}

@@

\section{Glossary of terms, acronyms and abbreviations}\label{ap:glossary}
The subjects involved in this article have numerous jargons, acronyms and abbreviations. Table~\ref{tab:glos} should help readers as a concise references.
\begin{table}[!h]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
  \footnotesize
  \vspace{-6mm}
  \centering
  \caption{Glossary for current article}
  \begin{tabular}{||l|p{5cm}|p{9cm}||}\hline
      {\bf term} & {\bf meaning} & {\bf further information} \\\hline\hline
      \aan  & Algorithmic Autoregulation & a platform for personal transparency, sharing ongoing work and proving dedication \\\hline
      \bfo  & Basic Formal Ontology & an upper ontology supporting information retrieval, analysis and integration in scientific and other domains \\\hline
      \cidadedemocratica  & a Brazilian civil society participatory portal & -//- \\\hline
      \dbpedia  & DBpedia is a crowd-sourced community effort to extract structured information from Wikipedia & consists of an ontological organization and data \\\hline
      \etherpad  & a web-based collaborative real-time editor, allowing authors to simultaneously edit a text document & -//- \\\hline
      \facebook & an online social networking service & -//-  \\\hline
      \foaf  & Friend Of A Friend & an ontology devoted to linking people and information using the Web, \foaf\ is a core ontology of the web semantic/linked data academic community \\\hline
      \html  & HyperText Markup Language & the standard markup language used to create Web pages \\\hline
      \http  & Hypertext Transfer Protocol & an application protocol for distributed, collaborative, hypermedia information systems. It is the foundation of data communication for the World Wide Web \\\hline
      \ict  & Information and communications technology  & often used as an extended synonym for information technology (IT) \\\hline
      \iri  & Internationalized Resource Identifier & a new internet standard to extend upon the existing uniform resource identifier (\uri) scheme, where \iri s are always utf-8 \\\hline
      \lod  & Linked Open Data & a human legacy of open and linked data \\\hline
      \mysql  & a widely used open-source relational database management system & -//-\\\hline
      \ngo  & Non-Governmental Organization & a term commonly used for an organization that is neither a part of a government nor a conventional for-profit business \\\hline
      \node  & an open source, cross-platform runtime environment for server-side and networking applications & applications are written in JavaScript  \\\hline
      \obda  & Ontology-Based Database Access & a general term for accessing databases through ontological criteria \\\hline
      \obs  & Social Library Ontology & from the Brazilian name Ontologia da Biblioteca Social \\\hline
      \ocd  & Cidade Democr\'atica Ontology & from the Brazilian name Ontologia do Cidade Democr\'atica \\\hline
      \ogp  & Open Government Partnership & an international organization promoting multilateral initiative and seeking strong commitments from participating government institutions to promote transparency, increase civic participation, fight corruption, and harness new technologies to make government more open, effective, and accountable \\\hline
      \ontologiaa  & \aan\ Ontology. &  the name is a derivative from the Brazilian ``Ontologia do \aan''. It is small, simple and entirely linked to upper ontologies (classes and properties) \\ \hline
      \ontop  & a platform to query databases as virtual \rdf\ graphs using \sparql\ & -//- \\\hline
      \opa  & \participa\ Ontology & from the Brazilian name Ontologia do \participa \\\hline
      \ops  & Ontology of Social Participation & Acronym from the Brazilian name: Ontologia de Participa\c{c}\~ao Social \\\hline
      \owl  & Web Ontology Language & for authoring ontologies \\\hline
      \participa  & the Brazilian federal participatory portal & -//- \\\hline
      \pubby  & A Linked Data Front-end for dereferencing \uri s & -//- \\\hline
      \python  & a widely used general-purpose, high-level programming language & known as an easy scripting language among researchers, developers and hackers \\\hline
      \quest  & the \sparql\ engine/reasoner that comes with \ontop & -//- \\\hline
      \rdf  & Resource Description Framework & a standard model for data interchange on the Web \\\hline
      \serpro  & Brazilian Federal Service of Data Processing & the biggest government-owned corporation of IT services of Brazil \\\hline
      \skos  & Simple Knowledge Organization System & a \wwwc recommendation designed for representation of thesauri, classification schemes, taxonomies, subject-heading systems \\\hline
      \sparql  & \sparql\ Protocol and \rdf\ Query Language & an \rdf\ query language  \\\hline
      \onu  & United Nations & an intergovernmental organization to promote international co-operation \\\hline
      \pnud  & United Nations Development Programme & the United Nations' global development network \\\hline
      \urll  & Uniform Resource Locator & also known as a web address, particularly when used with \http \\\hline
      \vbs  & Social Library Vocabulary & from the Brazilian name Vocabulário da Biblioteca Social \\\hline
      \vcps  & Common Vocabulary of Social Participation & Acronym from the Brazilian Vocabul\'ario Comum de Participa\c{c}\~ao Social\\\hline
      \wwwc     & World Wide Web Consortium & the main international standards organization for the World Wide Web \\\hline
\end{tabular}
  \label{tab:glos}
\end{adjustwidth}
\end{table}

>>>>

\begin{table*}
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
  \centering
  \caption{New classes considered for expansion of the \ops. The taxonomic organization of these classes, within \ops\ can be observed in Figure~\ref{fig:owlExp}. Further information is in Section~\ref{downwards}.}
  \begin{tabular}{|l|l|p{5cm}|p{5.7cm}|}\hline
{\bf new class} & {\bf subclass of} & {\bf description} & {\bf further notes} \\\hline\hline
SocialNetwork & Organization & a social structure made up of social actors (such as individuals or organizations) and a set of dyadic ties between these actors & --//--\\\hline
FreeScaleNetwork & SocialNetwork & a network whose connectivity follows a power law & disjoint with UniformrandomNetwork and GeographicNetwork \\ \hline
ErdosRenyiNetwork & SocialNetwork & also known as Poisson network, this network sets, with equal propability, an edge between each pair of nodes & disjoint with FreeScaleNetwork and GeographicNetwork\\\hline
GeographicNetwork & SocialNetwork & a network whose connectivity is related to the distance of nodes in a metric space & Disjoint with both FreeScaleNetwork and ErdosRenyiNetwork \\\hline
SmallWorldNetwork & SocialNetwork & a network where most nodes can be reached from other nodes with few hops or steps & not disjoint with FreeScaleNetwork, ErdosRenyiNetwork and GeographicNetwork\\\hline\hline
InformalOrganization & Organization & an organization that is not formalized & disjoint with Intitution \\ \hline
Mob & InformalOrganization & a crowd of individuals & --//-- \\\hline
GiantMob & Mob & a crowd with more than 10,000 individuals & --//--\\\hline
DownloadedMob & Mob & a Mob convoqued by a network & this is a defined class, by being a network and being the subject of the relation convoquedBy with object Network \\ \hline\hline
Institution & Organization & a mechanism of social order that governs a set of individuals & disjoint with InformalOrganization \\\hline
PublicInstitution & Institution & an institution backed through public funds and controlled by the state & disjoint with Private Institution \\ \hline
PrivateInstitution & Institution & an institution backed through private fundings and controlled by private parties & disjoint with PublicInstitution \\ \hline
AcademicInstitution & Institution & an institution dedicated to education and research, which grants academic degrees & --//-- \\ \hline
NGO & Institution & a legally consituted corporation created by natural or legal people that operate independently from any form of government & --//-- \\\hline
SpuriousInstitution & Institution & an institution that holds prominent illegitimate or corrupt characteristcs & --//-- \\\hline
ExoticInstitution & Institution & an institution that does not fit previous classes or is characterized by a very unique traces & --//-- \\\hline\hline
VoluntaryExecutor & Executor & an executor that receives no formal reward for the tasks & disjoint with PaidExecutor \\ \hline
PaidExecutor & Executor & an Executor that receives formal reward for the tasks accomplished & a defined class, being an Executor and the subject of a receivesFrom predicate with SocialActor as object\\ \hline
  \end{tabular}
  \label{ospFooClass}
\end{adjustwidth}
\end{table*}

@@

%\section{Glossary of terms, acronyms and abbreviations}\label{ap:glossary}
%The subjects involved in this article have numerous jargons, acronyms and abbreviations. Table~\ref{tab:glos} should help readers as a concise references.
%\begin{table}[!h]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
%  \footnotesize
%  \vspace{-6mm}
%  \centering
%  \caption{Glossary for current article}
%  \begin{tabular}{||l|p{5cm}|p{9cm}||}\hline
%      {\bf term} & {\bf meaning} & {\bf further information} \\\hline\hline
%      \aan  & Algorithmic Autoregulation & a platform for personal transparency, sharing ongoing work and proving dedication \\\hline
%      \bfo  & Basic Formal Ontology & an upper ontology supporting information retrieval, analysis and integration in scientific and other domains \\\hline
%      \cidadedemocratica  & a Brazilian civil society participatory portal & -//- \\\hline
%      \dbpedia  & DBpedia is a crowd-sourced community effort to extract structured information from Wikipedia & consists of an ontological organization and data \\\hline
%      \etherpad  & a web-based collaborative real-time editor, allowing authors to simultaneously edit a text document & -//- \\\hline
%      \facebook & an online social networking service & -//-  \\\hline
%      \foaf  & Friend Of A Friend & an ontology devoted to linking people and information using the Web, \foaf\ is a core ontology of the web semantic/linked data academic community \\\hline
%      \html  & HyperText Markup Language & the standard markup language used to create Web pages \\\hline
%      \http  & Hypertext Transfer Protocol & an application protocol for distributed, collaborative, hypermedia information systems. It is the foundation of data communication for the World Wide Web \\\hline
%      \ict  & Information and communications technology  & often used as an extended synonym for information technology (IT) \\\hline
%      \iri  & Internationalized Resource Identifier & a new internet standard to extend upon the existing uniform resource identifier (\uri) scheme, where \iri s are always utf-8 \\\hline
%      \lod  & Linked Open Data & a human legacy of open and linked data \\\hline
%      \mysql  & a widely used open-source relational database management system & -//-\\\hline
%      \ngo  & Non-Governmental Organization & a term commonly used for an organization that is neither a part of a government nor a conventional for-profit business \\\hline
%      \node  & an open source, cross-platform runtime environment for server-side and networking applications & applications are written in JavaScript  \\\hline
%      \obda  & Ontology-Based Database Access & a general term for accessing databases through ontological criteria \\\hline
%      \obs  & Social Library Ontology & from the Brazilian name Ontologia da Biblioteca Social \\\hline
%      \ocd  & Cidade Democr\'atica Ontology & from the Brazilian name Ontologia do Cidade Democr\'atica \\\hline
%      \ogp  & Open Government Partnership & an international organization promoting multilateral initiative and seeking strong commitments from participating government institutions to promote transparency, increase civic participation, fight corruption, and harness new technologies to make government more open, effective, and accountable \\\hline
%      \ontologiaa  & \aan\ Ontology. &  the name is a derivative from the Brazilian ``Ontologia do \aan''. It is small, simple and entirely linked to upper ontologies (classes and properties) \\ \hline
%      \ontop  & a platform to query databases as virtual \rdf\ graphs using \sparql\ & -//- \\\hline
%      \opa  & \participa\ Ontology & from the Brazilian name Ontologia do \participa \\\hline
%      \ops  & Ontology of Social Participation & Acronym from the Brazilian name: Ontologia de Participa\c{c}\~ao Social \\\hline
%      \owl  & Web Ontology Language & for authoring ontologies \\\hline
%      \participa  & the Brazilian federal participatory portal & -//- \\\hline
%      \pubby  & A Linked Data Front-end for dereferencing \uri s & -//- \\\hline
%      \python  & a widely used general-purpose, high-level programming language & known as an easy scripting language among researchers, developers and hackers \\\hline
%      \quest  & the \sparql\ engine/reasoner that comes with \ontop & -//- \\\hline
%      \rdf  & Resource Description Framework & a standard model for data interchange on the Web \\\hline
%      \serpro  & Brazilian Federal Service of Data Processing & the biggest government-owned corporation of IT services of Brazil \\\hline
%      \skos  & Simple Knowledge Organization System & a \wwwc recommendation designed for representation of thesauri, classification schemes, taxonomies, subject-heading systems \\\hline
%      \sparql  & \sparql\ Protocol and \rdf\ Query Language & an \rdf\ query language  \\\hline
%      \onu  & United Nations & an intergovernmental organization to promote international co-operation \\\hline
%      \pnud  & United Nations Development Programme & the United Nations' global development network \\\hline
%      \urll  & Uniform Resource Locator & also known as a web address, particularly when used with \http \\\hline
%      \vbs  & Social Library Vocabulary & from the Brazilian name Vocabulário da Biblioteca Social \\\hline
%      \vcps  & Common Vocabulary of Social Participation & Acronym from the Brazilian Vocabul\'ario Comum de Participa\c{c}\~ao Social\\\hline
%      \wwwc     & World Wide Web Consortium & the main international standards organization for the World Wide Web \\\hline
%\end{tabular}
%  \label{tab:glos}
%\end{adjustwidth}
%\end{table}
